Response to the defense feedback

### 2021-06-03 SupplementaryMaterial/Acknowledgments.tex
Updates from Overleaf

The members of my committee, Peng Liu, Sencun Zhu, Benjamin Hanrahan, and James Larus, provided helpful comments on my dissertation. Prof. Liu and Prof. Zhu greatly improved this dissertation with their comments from a security research angle. Prof. Hanrahan and Prof. Larus helped me improve the grammar of my dissertation proposal and my dissertation. Prof. Larus is a senior researcher and my last English teacher. I learned a lot on the written English from him.  His comments on the early draft are also very close to what I got from reviewers later. However, I did not take his comments seriously at the very beginning.

@@

Finally, I would like to thank my parents for their continuous emotional and financial support. My parents always hope that I can study in a university that is near to them. However, they still expressed their full support for me when I decided to come to U.S. as a graduate student.

>>>>

The members of my committee, Peng Liu, Sencun Zhu, Benjamin Hanrahan, and James Larus, provided helpful comments on my dissertation. Prof. Liu and Prof. Zhu greatly improved this dissertation with their comments from a security research angle. Prof. Hanrahan and Prof. Larus helped me improve the grammar of my dissertation proposal and my dissertation. Prof. Larus is a senior researcher and my last English teacher. I learned a lot on the written English from him. I am extremely grateful for his wise counsel.  Jim's comments on the early draft are also very close to what I got from reviewers later. However, I did not take his comments seriously at the very beginning.

@@

Finally, I would like to thank my parents for their continuous emotional and financial support. My parents always hope that I can study in an institution that is near to them. However, they still expressed their full support for me when I decided to come to U.S. as a graduate student.
